Continuous Generalization of Buildings

### 2017-08-10 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
basically finished programming. construct cover of buildings by iteratively merging dilated buildings

\newcommand{\myabstract}{We proposed a method to continuous 
	generalization of buildings from given start scale to any smaller goal 
	scale. 
	%
	If several buildings are close to each other at the start 
	scale, we bridge them by line segments and take the merge of these 
	buildings 
	and bridges as one building.
	For each building, either an original one or a merged one, at the start 
	scale, 
	we generate its target shape at 
	the goal scale by enlarging and simplifying. Then we grow the  
	building to the target shape. 
	%
	After finishing the growing, we take the goal scale as the 
	start scale and repeat our continuous generalization.
	\newline\indent
	Our contribution is as follows. First, the buildings 
	are enlarged continuously. At the same time, they are simplified. 
	Second, we ensure that the distance between any pair of two buildings is 
	always larger than a specified threshold.}

@@

We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. We found that Imai--Iri simplification 
algorithm \parencite{ImaiIri1988} fit our needs well.

>>>>

\newcommand{\myabstract}{We propose a method to continuously 
	generalize buildings from a given start scale to a smaller goal scale. 
	%
	If several buildings are close to each other at the start 
	scale, we bridge them by line segments and merge the several buildings into 
	one 
	building.
	For each building, either an original one or a merged one, at the start 
	scale, 
	we generate its target shape at 
	the goal scale by enlarging and simplifying. 
	Then we grow the building to the target shape.
	%
	After finishing the growing, we can take the goal scale as the 
	start scale and repeat the process.
	\newline\indent
	The advantages of our method are as follows. First, the buildings 
	are enlarged continuously. At the same time, they are simplified. 
	Second, we ensure that the distance between any pair of two buildings is 
	always larger than a specified threshold.}

@@

We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. We found that Imai--Iri 
algorithm \parencite{ImaiIri1988} fit our needs well.

Imai--Iri algorithm finds all the valid shortcuts, and then
